---
title: "Take-Home Exercise 03"
---

## **Our Task**

## **The Data**

# **1. Getting Started**

## **1.1 Loading R packages**

We load the following R packages using the `pacman::p_load()` function:

```{r}

pacman::p_load(tidyverse, ggrepel, patchwork, 
               ggthemes, hrbrthemes,
              ggridges, colorspace) 

```

## **1.2 Importing data**

The code chunk below imports the dataset into R environment by using [*`read_csv()`*](https://readr.tidyverse.org/reference/read_delim.html) function of [`readr`](https://readr.tidyverse.org/) package. **readr** is one of the tidyverse package.

Read the individual CSV files into data frames. Check that the structure of each data frame is the same.

```{r}
Titleinfo <- read_csv("data/Data_TitleInfo.csv")
```

```{r}
Studentinfo <- read_csv("data/Data_StudentInfo.csv")
```

```{r}
class1<- read_csv("data/Data_Submitrecord/SubmitRecord-Class1.csv")
```

```{r}
class2<- read_csv("data/Data_Submitrecord/SubmitRecord-Class2.csv")
```

```{r}
class3 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class3.csv")
```

```{r}
class4 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class4.csv")
```

```{r}
class5 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class5.csv")
```

```{r}
class6 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class6.csv")
```

```{r}
class7 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class7.csv")
```

```{r}
class8 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class8.csv")
```

```{r}
class9 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class9.csv")
```

```{r}
class10<- read_csv("data/Data_Submitrecord/SubmitRecord-Class10.csv")
```

```{r}
class11 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class11.csv")
```

```{r}
class12 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class12.csv")
```

```{r}
class13 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class13.csv")
```

```{r}
class14 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class14.csv")
```

```{r}
class15 <- read_csv("data/Data_Submitrecord/SubmitRecord-Class15.csv")
```


## **Check missing values**
